Modal operators for a constructive account of well quasi-orders

### 2025-02-26 slides-abmv2024.tex
Slides finished
typo

    \emph{Proof.} Let~$K \defeq \{ n \in \NN \,|\, \neg \exists m > n\_
    \alpha\,n \leq \alpha\,m \}$ the set of indices of those terms which cannot
    appear as the first component of a good pair. If~$K$ is in bijection
    with~$\NN$, there is a subsequence~$\alpha\,k_0 \leq \alpha\,k_1 \leq
    \ldots$ with~$k_0, k_1, \ldots \in K$. As~$X$ is well\sinf, this sequence
    is good, a contradiction.

@@

    For partial maps~$\alpha$, by~$\alpha\,n\,\downarrow$ we mean that~$\alpha$
    is defined on the input~$n$. If~\bad{\textsc{lem}} is available, then a
    partial map such that~$\neg\neg(\alpha\,n\,\downarrow)$ for all~$n \in \NN$
    is already a total map, but without~\bad{\textsc{lem}} the hypothesis
    well\sinf does not have anything to say about such a partially-defined
    sequence.

    If~\bad{\textsc{dc}} is available, then every multivalued map contains a
    singlevalued map, but again without~\bad{\textsc{dc}} the hypothesis well\sinf
    does not have anything to say about multivalued sequences.
  }

@@

    \textbf{Prop.} Let~$X$ and~$Y$ be well\ind quasi-orders. Then~$X \times Y$
    is well.

    \emph{Lemma.} Let~$\alpha = (\beta,\gamma) : \NN \to X \times Y$ be a sequence in an
    arbitrary topos. We need to show that~$\alpha$ is good. It suffices to
    prove that \emph{somewhere}, $\alpha$ is good, as goodness is a geometric
    implication (in fact even a geometric formula). Without loss of generality,
    we may suppose~\textsc{lem} as it holds \emph{somewhere}.

>>>>

    \emph{Proof.} Let~$K \defeq \{ n \in \NN \,|\, \neg \exists m > n\_
    \alpha\,n \leq \alpha\,m \}$ be the set of indices of those terms which cannot
    appear as the first component of a good pair. If~$K$ is in bijection
    with~$\NN$, there is a subsequence~$\alpha\,k_0 \leq \alpha\,k_1 \leq
    \ldots$ with~$k_0, k_1, \ldots \in K$. As~$X$ is well\sinf, this sequence
    is good, a contradiction.

@@

    For partial maps~$\alpha$, by~$\alpha\,n\,\downarrow$ we mean that~$\alpha$
    is defined on the input~$n$. If~\bad{\textsc{lem}} is available, then a
    partial map such that~$\neg\neg(\alpha\,n\,\downarrow)$ for all~$n \in \NN$
    is already a total map, but without~\bad{\textsc{lem}} the hypothesis
    well\sinf{} does not have anything to say about such a partially-defined
    sequence.

    If~\bad{\textsc{dc}} is available, then every multivalued map contains a
    singlevalued map, but again without~\bad{\textsc{dc}} the hypothesis well\sinf{}
    does not have anything to say about multivalued sequences.
  }

@@

    \textbf{Prop.} Let~$X$ and~$Y$ be well\ind quasi-orders. Then~$X \times Y$
    is well\ind.

    \emph{Proof.} Let~$\alpha = (\beta,\gamma) : \NN \to X \times Y$ be a sequence in an
    arbitrary topos. We need to show that~$\alpha$ is good. It suffices to
    prove that \emph{somewhere}, $\alpha$ is good, as goodness is a geometric
    implication (in fact even a geometric formula). Without loss of generality,
    we may suppose~\textsc{lem} as it holds \emph{somewhere}.
